### 2013-02-14 doc/xps2013/proposal.tex
commit to merge

Language and compiler support are instrumental in making Grappa usable to a wide audience of software developers. We envision language and compiler support can tackle a wide variety of challenges:

@@

\paragraph{Concurrency Control: } Having too few tasks multiplexed per core fails to tolerate fully the latency; having too many increases memory and cache footprints, resulting in excess cache misses or exhausting physical memory unnecessarily.  Currently, we choose a number at program instantiation:  experiments so far have shown evidence of a broad sweet-spot, though it is of course varies as a function of application behavior.  At compile-time, we could estimate the number of tasks required based on the density of remote operations and hard-coded measurements of system characteristics; at runtime we can adjust the number of tasks dynamically based on real-time measurement of processor counters.  Exploring these directions may lead to even more robust performance.

Presently we are starting work on this language and compiler support.  We are basing our effort on the LLVM~\cite{llvm} infrastructure.

>>>>

Language and compiler support are instrumental in making Grappa usable to a
wide audience of application developers. We plan to use the LLVM~\cite{llvm}
infrastructure. Below we describe the specific aspects we plan to tackle.

@@

\paragraph{Task load control:} Having too few tasks per core fails to tolerate
fully the latency; having too many increases overheads unnecessarily.
Currently, we choose a number at program instantiation: experiments so far
have shown evidence of a broad sweet-spot, though it is of course varies as a
function of application behavior and input data. At compile-time, we might be
able to estimate the number of tasks required based on the density of remote
operations and system parameters (e.g., memory size, network latency, etc.);
at runtime we can adjust the number of tasks dynamically based on periodic
performance assessments.

% Presently we are starting work on this language and compiler support.  We are basing our effort on the LLVM~\cite{llvm} infrastructure.
